### 2017-06-20 manuscript/manuscript.Rmd
Remove unnecessary whitespace in code examples.

```bash
# Ignore everything inside the 'admin' folder
admin/

# Ignore all .pdf files in the 'manuscript' folder
manuscript/*.pdf

# Ignore a specific file in a specific folder
analysis/sandbox.R
```

@@

```bash
$ git add .gitignore
$ git commit -m "Added .gitignore file"

$ git add .
$ git commit -m "Completed power analysis"
```

>>>>

```bash
# Ignore everything inside the 'admin' folder
admin/
# Ignore all .pdf files in the 'manuscript' folder
manuscript/*.pdf
# Ignore a specific file in a specific folder
analysis/sandbox.R
```

@@

```bash
$ git add .gitignore
$ git commit -m "Added .gitignore file"
$ git add .
$ git commit -m "Completed power analysis"
```
